---
title: "Final_Project"
author: "Christopher_Zdyrski"
date: "4/13/2021"
output: html_document
---
#This file is to make the figures found in the Kort et al. paper figure 2a, 2b, and 6.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Install packages
```{r}
install.packages("tidyverse")
```

#Load in librarys
```{r}
library(readxl)
library(ggplot2)
library(tidyverse)
```

#Open data file
```{r}
#This is the data file we will use
raw_data <- read_excel("Copy of DMCs_Dryad.xlsx")
raw_data <- data.frame(raw_data)
```

###Look at dimensions of the files
```{r}
#Analyze the raw_data file
head(raw_data)
dim(raw_data)
str(raw_data)
colnames(raw_data)
```

###We have to sort and combine data files somehow
```{r}
#Sort and rearrange the raw_data file

```

#"Significant DMCs were identified between (a) low‐, mid‐ and high‐altitude samples (hereafter “altitudinal DMCs”)
#(b) the three distance European samples (hereafter “spatial DMCs”), and (c) the two soil moisture treatments (hereafter “drought DMCs”)."
#
#Feel free to change anything!
#


#Make Figure 2a
##You have to include state=identity when working with excel files
```{r}
#HAVE TO CHANGE X COLUMN TO SOMETHING ELSE
fig_two_a <- (ggplot(data=raw_data, aes(Type, meth.diff, fill=Context)) +
                
  #This is to work with excel files         
  geom_bar(stat='identity') +
    
  #Add and format title
  ggtitle("Figure 2a") +
  theme(plot.title = element_text(hjust = 0.5)) +

  #Add and format axis
  labs(x = "Altitude", y = "Log10 DMC Count") +
  #NOT WORKING
  theme(axis.text.x = element_text(angle = 45)) +

  #this is to add the legend without a title
  theme_minimal()+
  theme(legend.title = element_blank()))

print(fig_two_a)
pdf("Plots/fig_two_a.pdf")
```

#Make Figure 2b
#THE COLUMNS IT IS PULLING DATA FROM ARE JUST PLACE HOLDER
```{r}
#Using column _______ for x axis and column _____ for y axis

#HAVE TO CHANGE Both COLUMNs TO SOMETHING ELSE
fig_two_b <- (ggplot(data=raw_data, aes(Type, meth.diff, fill=Context)) +
                
  #This is to work with excel files         
  geom_bar(stat='identity') +
    
  #Add and format title
  ggtitle("Figure 2b") +
  theme(plot.title = element_text(hjust = 0.5)) +

  #Add and format axis
  labs(x = "Altitude", y = "Δ Methylation") +
  #NOT WORKING
  theme(axis.text.x = element_text(angle = 45)) +

  #this is to add the legend without a title
  theme_minimal()+
  theme(legend.title = element_blank()))

print(fig_two_b)
pdf("Plots/fig_two_b.pdf")
```

#Make Figure 6
#Have to sort out CG, CHG and CHH
#THE COLUMNS IT IS PULLING DATA FROM ARE JUST PLACE HOLDER
```{r}
#Using column _______ for x axis and column _____ for y axis

#HAVE TO CHANGE Both COLUMNs TO SOMETHING ELSE
fig_six <- (ggplot(data=raw_data, aes(Type, meth.diff, fill=Context)) +
                
  #This is to work with excel files and a boxplot         
  geom_boxplot(stat='identity') +
    
  #Add and format title
  ggtitle("Figure 6, West to East") +
  theme(plot.title = element_text(hjust = 0.5)) +

  #Add and format axis
  labs(x = "Loss/Gain Position", y = "DMC Density") +
  #NOT WORKING
  theme(axis.text.x = element_text(angle = 45)) +

  #this is to add the legend without a title
  theme_minimal()+
  theme(legend.title = element_blank()))

print(fig_six)
pdf("Plots/fig_six.pdf")
```